Dynamical modeling of tidal streams

### 2014-01-09 tex/ms.tex
streams: add readthedocs link as alternative, add Binney to acks

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{amssymb,amsmath}
%\usepackage{caption}
%\DeclareCaptionLabelSeparator{dotemdash}{.--- }
%\captionsetup[figure]{labelformat=simple, labelsep=dotemdash}
%\usepackage{color,hyperref}
% hypertex insanity
%\definecolor{linkcolor}{rgb}{0,0,0.25}
%\hypersetup{
%  colorlinks=true,        % false: boxed links; true: colored links
%  linkcolor=linkcolor,    % color of internal links
%  citecolor=linkcolor,    % color of links to bibliography
%  filecolor=linkcolor,    % color of file links
%  urlcolor=linkcolor      % color of external links
%}
\newcounter{address}
\setcounter{address}{1}
%\usepackage{sidecap}
\setlength{\emergencystretch}{2em}%No overflowing references
\newcommand{\ie}{i.e.}
\newcommand{\etal}{et al.}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\eg}{e.g.}
\newcommand{\eqnname}{equation}
\newcommand{\Eqnname}{Equation}
\newcommand{\equationname}{\eqnname}
\renewcommand{\tablename}{Table}
\renewcommand{\figurename}{Figure}
\newcommand{\figurenames}{\figurename~s}
\newcommand{\sectionname}{$\mathsection$}
\newcommand{\normal}{\ensuremath{\mathcal{N}}}
\newcommand{\flag}[1]{\texttt{\lowercase{#1}}}
\newcommand{\feh}{\ensuremath{[\mathrm{Fe/H}]}}
\newcommand{\afe}{\ensuremath{[\alpha\mathrm{/Fe}]}}
\newcommand{\logg}{log g}
\newcommand{\Ro}{\ensuremath{R_0}}

@@

The full modeling and action--angle framework presented here is
available as part of the \emph{galpy} Galactic Dynamics
code\footnote{Available at
  \protect{\url{http://github.com/jobovy/galpy}}~.}. A tutorial on how
to use this code is given at
\[
\protect{\mathrm{\url{http://jobovy.github.io/galpy/streamdf.html}}}\,.
\]

@@

\acknowledgements It is a pleasure to thank David W. Hogg, Hans-Walter
Rix, Jason Sanders, and Scott Tremaine for helpful
discussions. J.B. was supported by NASA through Hubble Fellowship
grant HST-HF-51285.01 from the Space Telescope Science Institute,
which is operated by the Association of Universities for Research in
Astronomy, Incorporated, under NASA contract NAS5-26555. J.B.
acknowledges support from SFB 881 (A3) funded by the German Research
Foundation DFG.

>>>>

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{amssymb,amsmath}
\usepackage{color,hyperref}
% hypertex insanity
\definecolor{linkcolor}{rgb}{0,0,0.25}
\hypersetup{
  colorlinks=true,        % false: boxed links; true: colored links
  linkcolor=linkcolor,    % color of internal links
  citecolor=linkcolor,    % color of links to bibliography
  filecolor=linkcolor,    % color of file links
  urlcolor=linkcolor      % color of external links
}
\newcounter{address}
\setcounter{address}{1}
\setlength{\emergencystretch}{2em}%No overflowing references
\newcommand{\ie}{i.e.}
\newcommand{\etal}{et al.}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\eg}{e.g.}
\newcommand{\eqnname}{equation}
\newcommand{\Eqnname}{Equation}
\newcommand{\equationname}{\eqnname}
\renewcommand{\tablename}{Table}
\renewcommand{\figurename}{Figure}
\newcommand{\figurenames}{\figurename~s}
\newcommand{\sectionname}{$\mathsection$}
\newcommand{\normal}{\ensuremath{\mathcal{N}}}
\newcommand{\flag}[1]{\texttt{\lowercase{#1}}}
\newcommand{\feh}{\ensuremath{[\mathrm{Fe/H}]}}
\newcommand{\afe}{\ensuremath{[\alpha\mathrm{/Fe}]}}
\newcommand{\logg}{log g}
\newcommand{\Ro}{\ensuremath{R_0}}

@@

The full modeling and action--angle framework presented here is
available as part of the \emph{galpy} Galactic Dynamics
code\footnote{Available at
  \protect{\url{http://github.com/jobovy/galpy}}~.}. A tutorial on how
to use this code is given at\footnote{An alternative link is\\ \protect{\url{http://galpy.readthedocs.org/en/latest/streamdf.html}}~.}
\begin{center}
\protect{\url{http://jobovy.github.io/galpy/streamdf.html}}\,.
\end{center}

@@

\acknowledgements It is a pleasure to thank James Binney, David
W. Hogg, Hans-Walter Rix, Jason Sanders, and Scott Tremaine for
helpful discussions. J.B. was supported by NASA through Hubble
Fellowship grant HST-HF-51285.01 from the Space Telescope Science
Institute, which is operated by the Association of Universities for
Research in Astronomy, Incorporated, under NASA contract
NAS5-26555. J.B.  acknowledges support from SFB 881 (A3) funded by the
German Research Foundation DFG.
